Closing the gap between statistical and scientific workflows for improved forecasts in ecology

### 2025-03-27 forecastflows_outline.tex
adding some stuff not to forget

\item More details on ideal workflow:  walk through the different steps \textbf{(Figure 2)}

@@

\item complexity trap [mention uncertainty]

@@

@@

\item machine learning! If we do nothing, what's the point of not doing ML? ML $>$ process-based without question, and ML $>$ trends without mechanisms

@@

\item ML, benchmarking models are probably useful but should not be the core of our scientific practice, not the spirit!

>>>>

\item More details on ideal workflow:  walk through the different steps \textbf{(Figure 2)}, and emphasizes: not rigid structure, integration of everything,  iterate the process of science, explicit effort to recognize the uncertainties, 

@@

\item complexity trap [mention uncertainty], counterproductive, not always better performance

@@

\item a clear framework to support (or not) additional complexity and new parameters

@@

\item machine learning! If we change nothing, what's the point of not doing ML? ML $>$ process-based without question, and ML $>$ trends without mechanisms! Where theory is lacking, or where we are far from mechanistic understanding, you might as well do ML!
\item (ML has a way to collect and interpret large datasets...)

@@

\item ML (short-time forecast), benchmarking models are probably useful but should not be the core of our scientific practice, not the spirit!\\
$\rightarrow$ moving ecology in the right direction!
